Star-galaxy Classification Using Convolutional Neural Networks

### 2016-05-17 paper/main.tex
add spread model reference

ConvNets have recently achieved record-breaking results in many image
classification tasks~\citep{lecun2015deep} and have been quickly and widely
adopted by the computer vision community.
One of the main reasons for the success is that ConvNets are general-purpose
algorithms that are applicable to a variety of problems without the need for
designing a feature extractor.
The lack of requirement for feature extraction is a huge advantage \eg
when the task is to classify 1 000 classes in the ImageNet data
set~\citep{russakovsky2015imagenet},
as a good feature extractor for identifying images of cats would of little use
for classifying sailboats, and it is impractical to design a feature extractor
for each class.
However, if there already exists a good feature extractor for the problem
at hand, \eg the concentration parameter or the \texttt{SExtractor} software,
conventional machine learning algorithms that are proven to be effective,
such as TPC~\citep{carrascokind2013tpz, kim2015hybrid}, remain a viable option.
As the "no free lunch" theorem~\citep{wolpert1996lack} states,
there is no one model that works for every problem.
For the CFHTLenS data set, our ConvNet model outperforms TPC trained on the
output of \texttt{SExtractor}.
Since the SDSS catalog provides the concentration paramter that is highly
optmized for star-galaxy classification, TPC works better for SDSS.

>>>>

ConvNets have recently achieved record-breaking results in many image
classification tasks~\citep{lecun2015deep} and have been quickly and widely
adopted by the computer vision community.
One of the main reasons for the success is that ConvNets are general-purpose
algorithms that are applicable to a variety of problems without the need for
designing a feature extractor.
The lack of requirement for feature extraction is a huge advantage \eg
when the task is to classify 1 000 classes in the ImageNet data
set~\citep{russakovsky2015imagenet},
as a good feature extractor for identifying images of cats would of little use
for classifying sailboats, and it is impractical to design a feature extractor
for each class.
However, when there already exists a good feature extractor for the problem
at hand, \eg the concentration parameter, the weight-averaged
\texttt{spread\_model} parameter from the Dark Energy
Survey~\citep{desai2012blanco,crocce2016galaxy},
or even the \texttt{SExtractor} software,
conventional machine learning algorithms that are proven to be effective,
such as TPC~\citep{carrascokind2013tpz, kim2015hybrid}, remain a viable option.
As the "no free lunch" theorem~\citep{wolpert1996lack} states,
there is no one model that works for every problem.
For the CFHTLenS data set, our ConvNet model outperforms TPC trained on the
output of \texttt{SExtractor}.
Since the SDSS catalog provides the concentration paramter that is highly
optmized for star-galaxy classification, TPC works better for SDSS.
